### 2022-03-21 sections/background_estimation.tex
update figure 1 with log-scale

Most background processes are modelled using MC simulation.
After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
Small contributions arise from single-top-quark, $W/Z$+jets, multi-jet and diboson ($WW,WZ,ZZ$) production, as well as from the associated 
production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
with prompt leptons, i.e.\ those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
In the simulation, the top-quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
and the Higgs boson is forced to decay into $H\to \tau\tau$ with branching ratio calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
Backgrounds with non-prompt light leptons (electron or muon), with photons or jets misidentified as electrons, or with jets misidentified as tau candidates, 
generically referred to as \texttt{fake} leptons, are estimated using data-driven methods. 
The background prediction is further improved during the statistical analysis by performing a likelihood 
fit to data using several signal-depleted control regions as shown in Table~\ref{tab:srcr}.
The events with one light lepton, two same-sign $\had$, and one $b$-jet, are also selected, enter in a validation region (VR) for the background estimation in the leptonic channels. 
%-------------------------------------------------------------------------------
%\subsection{Backgrounds with fake leptons}
%\label{sec:fakeleptons}
%-------------------------------------------------------------------------------
\subsection{Backgrounds with fake tau leptons}
\label{sec:faketaus}
The background with one or more fake tau candidates mainly arises from $\ttbar$ or
multi-jet production, depending on the search channels.
Studies based on simulation show that, for all the above processes, fake tau candidates primarily result from the
misidentification of light jets and $b$-quark jets.
It is also found that the fake rate decreases for all jet flavours as the tau candidate $\pt$ increases.

>>>>

Most background processes are modelled using MC simulation.
After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
Small contributions arise from single-top-quark, $W/Z$+jets, multi-jet and diboson ($WW,WZ,ZZ$) production, as well as from the associated 
production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
with prompt leptons, i.e.\ those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
In the simulation, the top-quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
and the Higgs boson is forced to decay into $H\to \tau\tau$ with branching ratio calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
Backgrounds with non-prompt light leptons (electron or muon), with photons or jets misidentified as electrons, or with jets misidentified as tau candidates, 
generically referred to as \texttt{fake} leptons, are estimated using data-driven methods. 
The background prediction is further improved during the statistical analysis by performing a likelihood 
fit to data using several signal-depleted control regions as shown in Table~\ref{tab:srcr}.
The events with one light lepton, two same-sign $\had$, and one $b$-jet, are also selected, providing a validation region (VR) for the background estimation in the leptonic channels. 
%-------------------------------------------------------------------------------
%\subsection{Backgrounds with fake leptons}
%\label{sec:fakeleptons}
%-------------------------------------------------------------------------------
\subsection{Backgrounds with fake tau leptons}
\label{sec:faketaus}
The background with one or more fake tau candidates mainly arises from $\ttbar$ or
multi-jet production, depending on the search channels.
Studies based on simulation show that, for all the above processes, fake tau candidates primarily result from the
misidentification of light jets and $b$-quark jets.
It is also found that the fake rate decreases for all jet flavours as the tau candidate $\pt$ increases.

### 2022-03-21 sections/bdt_Htautau.tex
update figure 1 with log-scale

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}\\
(d) & (e) \\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}\\
(f) & (g) \\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (``Pre-Fit'') showing 
  the expected background and $tuH$ signals after applying fake factors in the following SRs: $t_{\ell}\thadhad$ (a),
  $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_h\thadhad$-2j (f), and $t_h\thadhad$-3j (g).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled using a normalization factor of 2 to 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:taupt_prefit}
\end{figure}

>>>>

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l2tau1bnj_os_log_.pdf} &
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b1j_ss_log_.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_ss_log_.pdf}\\
(a) & (b) & (c) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b2j_os_log_.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg1l1tau1b3j_os_log_.pdf}\\
(d) & (e) \\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b2jos_log_.pdf}&
\includegraphics[page=1,width=0.29\textwidth]{figures/new_pt/log_or_nolog/tuH_reg2mtau1b3jos_log_.pdf}\\
(f) & (g) \\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{Leading $\thad$ $\pt$  distributions obtained before the fit to data (``Pre-Fit'') showing 
  the expected background and $tuH$ signals after applying fake factors in the following SRs: $t_{\ell}\thadhad$ (a),
  $t_{\ell}\tauhad$-1j (b),  $t_{\ell}\tauhad$-2j (c), $t_h\tlhad$-2j (d), $t_h\tlhad$-3j (e), $t_h\thadhad$-2j (f), and $t_h\thadhad$-3j (g).
 The total size of the statistical and systematic uncertainties of the background prediction is indicated by the hatched band.
 %The uncertainty band includes both the statistical and systematic uncertainties in the background prediction.
 Overflow events are included in the last bin. ``Other MC'' (``Rare'') includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) channel. The $tuH$ signal is scaled using a normalization factor of 2 to 50.   
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the data to prediction ratio.}
\label{fig:taupt_prefit}
\end{figure}
